Developing a preprint culture in biology

### 2012-10-05 ms.tex
Reorganizing and editing the Case for Public Preprints section

The first and most often discussed advantage of arXiv and open preprints is
speed (Figure~\ref{fig:map}). The time between submission and the official
publication of a manuscript can be measured in months, sometime in years. For
all this time, the research is known only to a select few: colleagues, editors,
reviewers.  Thus, the science cannot be used, discussed, or reviewed by the
wider scientific community.  This stage of manuscript preparation is a problem
for both scientists and publishers.  Manuscripts that are unknown cannot be used
and thus take more time to be cited. It has been shown that high-energy physics,
with its high arXiv submission rate, had the highest immediacy among physics and
mathematics \cite{pra05}. Immediacy measures how quickly articles are cited.

Furthermore, the review process as a whole is critically over-loaded, because
as the number of active scientists increases, because the pressure to publish
increases, and because of an effect dubbed ``the tragedy of the reviewers
commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the whole
process all over again.  Initiatives to reduce time from submission to
publication have emerged across the scientific community. Rohr et al.
\cite{roh09} called for the recycling and reuse of peer-reviews:
by attaching previous reviews and detailed replies to a new submission, both
the editor and the referees can gauge the work done on the manuscript, and
perhaps evaluate it with less prejudice. In a similar way, the \emph{Peerage
of Science} initiative allows authors to seek anonymous pre-review by their
peers. Some journals now accept to publish papers which received good
evaluations, with \emph{Animal Biology} having recently accepted first a paper
reviewed entirely with the \emph{Peerage of Science} \cite{abb12}, effectively
outsourcing the review process. A widespread use of preprint servers can
achieve the same goal of reducing the time spent in review. By putting a
manuscript for open comments and criticisms, the authors will receive valuable
feedback and can improve the version which will be submitted. With a rich
enough community of scientists depositing preprints, and commenting on them,
the process of an open pre- review can become widespread and will overall
increase the quality of first submissions.

@@

Public preprint servers offer a much fairer way to establish intellectual
priority by making the work available when done. Some manuscripts will spend
much more time in the review process than others. Surprisingly, there is a
perception in biology that public preprints make it easier to steal ideas, as if
a scientific idea was only complete once published in a peer-reviewed journal
\cite{gin11}. Ironically, mathematicians and physicists have embraced arXiv in
part to establish priority in a fair way \cite{gin11,cal12}.

Prepublication reviews by a small network of colleagues is an important part of
the scientific process, attested by the fact that nearly all published papers
acknowledge comments by people not listed as co-authors.  Preprint servers
simply offer a way to extend this network of colleagues to the entire scientific
community. It ensures that science is not constrained by small networks of
scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
democratic reasons: he wanted everyone from students in small universities to
Ivy-League professors to have access to the most recent scientific \emph{ideas}.
Ginsparg's revolutionary idea was simply to use the power of the internet for
preprints, not just for the end product, so the scientific process can be open
as soon as possible.

>>>>

The first and most often discussed advantage of arXiv and open preprints is
speed (Figure~\ref{fig:map}). The time between submission and the official
publication of a manuscript can be measured in months or even years. During
this time, the research is known only to a select few: colleagues, editors,
reviewers.  Thus, the science cannot be used, discussed, or reviewed by the
wider scientific community.  If the science being published is a year
or more behind the cutting edge, then science will progress more slowly. While
conferences and informal sharing of ideas among research groups may ameliorate
this issue, this type of communication is inherently limited to a restricted
subset of scienctists. Posting preprints ensures that science is not
constrained by small networks of scientists exchanging ideas.  Paul Ginsparg
created arXiv.org in part for democratic reasons: he wanted everyone from students
in small universities to Ivy-League professors to have access to the most recent
scientific \emph{ideas}. Ginsparg's revolutionary idea was simply to use the power
of the internet for preprints, not just for the end product, so the scientific
process can be open to all as soon as possible.

Posting manuscripts as preprints also has the potential to result in higher
quality science, by allowing for pre-publication feedback
from a large pool of reviewers. Prepublication reviews by a small network of
colleagues are common in the biological sciences and are an important part of
the scientific process. These "friendly" reviews increases the chances of errors
being caught prior to publication, allow errors to be identified
prior to spending months in review, and allows authors to improve how they
communicate the results of their research by modifying their writing in response
to early feedback. Preprint servers offer a way to extend this network of
colleagues to the entire scientific
community, increasing the number of opportunities for review and revision
prior to publication, and resulting in higher quality submissions and publications.
As such, preprints can be seen as an
integral aspect of a vigorous peer-review process \cite{hoc12}.

%It is unclear to me whether we should keep this full paragraph or try to distill
%it to a sentence or two at the end of the previous paragraph.
Furthermore, the formal peer-review process as a whole is critically over-loaded. As
the number of active scientists increases and the pressure to publish
increases, it has become increasingly difficult for journals to find
reviewers \cite{hoc09}.  At the same time, rejection rates are high in most journals
\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the
process over again at another journal. As a result, initiatives to reduce time from submission to
publication have emerged across the scientific community. Rohr et al.
\cite{roh09} called for the recycling and reuse of peer-reviews:
by attaching previous reviews and detailed replies to a new submission, both
the editor and the referees can gauge the work done on the manuscript, and
perhaps evaluate it with less prejudice. In a similar way, the \emph{Peerage
of Science} initiative allows authors to seek anonymous pre-review by their
peers. Some journals now accept to publish papers which received good
evaluations, with \emph{Animal Biology} having recently accepted first a paper
reviewed entirely with the \emph{Peerage of Science} \cite{abb12}, effectively
outsourcing the review process. A widespread use of preprint servers can
achieve the same goal of reducing the time spent in review. By allowing
open comments and criticisms prior to submission, the authors will receive valuable
feedback and can improve the version which will be submitted. With a rich
enough community of scientists depositing preprints, and commenting on them,
the process of an open pre-review can become widespread and will overall
increase the quality of first submissions.

@@

Finally, public preprint servers offer a fair way to establish intellectual
priority by making the work available when immediately after it is complete.
Some manuscripts will spend much more time in the review process and/or in
production after acceptance, than others. This means that
that publication and acceptance dates do not accurately characterize who
came up with an idea first. For this reason, mathematicians and physicists
have embraced arXiv in part to establish priority in a fair way \cite{gin11,cal12}.
In contrast, there is a surprising perception in biology that public preprints
make it easier to steal ideas. Since there is no evidence that this has happened
in the numerous other fields that have adopted preprint servers, and since preprint
servers create a clear record of who had the idea first, and when, this would
appear to be a largely unfounded concern.
%I'm torn over whether to keep the biology part in this paragraph where it is 
%topically related, or to move it down into the biological sciences part of the ms
